District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa

### 2023-08-31 paper/paper.tex
Add section on age at circumcision, still to be filled in
Updates from Overleaf

>>>>

\subsection{Subnational Heterogeneity in Age at Medical and Traditional Circumcision}
\label{sec:org92e0f37}

Fill in! Take some of the last section and put it here.

% Geofaceted plot of 2020 coverage by age
\begin{figure}[H]
    \centering
    \includegraphics[width=.9\linewidth]
    {plots/05_map_plot_mean_circ_age.png}
    \caption{\emph{(A) Estimated distinct-level age at circumcision in 2020 in 33 sub-Saharan African countries. Maps show mean medical male circumcision (MMC) and mean traditional male circumcision (TMC) age. Countries without estimates are in grey. Mean circumcision ages are binned into three distinct groups: 0-10, 11-20 and over 20. (B) Scatterplot of district-level mean traditional male circumcision age versus mean medical male circumcision age. A diagonal dashed line passes through the origin and (30, 30). Points representing each district are coloured by whether their country is a Voluntary Male Medical Circumcision (VMMC) priority country.}}
\end{figure}

% stimated percentage of men aged 15-29 years who were circumcised sub-nationally in 33 sub-Saharan African countries in 2006 and 2020, as well as the difference in coverage between the two years. Maps show total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC), respectively. Countries with no information on circumcision type are grey in the Medical and Traditional plots, while countries with no circumcision estimate are grey in all
